\documentclass[uplatex,a4paper,10pt]{jsarticle}
\usepackage{amsmath,amsthm,amssymb}
\usepackage{multicol}
\usepackage{url}
\usepackage[subrefformat=parens]{subcaption}
\captionsetup{compatibility=false}
\usepackage[dvipdfmx]{graphicx}
%\usepackage[headsep=10pt, head=30pt,foot=10pt]{geometry}
\usepackage{epsf}
\usepackage{bm}
\setlength{\columnseprule}{0.3pt}
\begin{document}
\begin{center}
\vspace*{3cm} \underline{\HUGE 卒業論文中間報告 }\\
\vspace{1cm}
\bf{ \Huge タイトル\\}
\vspace{3cm}
\huge 2022年9月30日提出 \\
\vspace{3cm}
\end{center}
\begin{minipage}{0.4\hsize}
\hspace{1zw}
\end{minipage}
\begin{center}
\begin{minipage}{0.7\hsize}
{\huge 指導教員　　　廣瀬　明　教授\\}
\vspace{1cm}\\
\centering
{\huge 電気電子工学科\\}
{\huge 03-210478　上野俊樹}
\end{minipage}
\end{center}


\newpage
\tableofcontents

\newpage 

\section{序章}

\subsection{背景}


\subsection{目的}

\section{従来手法と基本原理}

\subsection{計測方法}



\subsection{特徴良ベクトルの抽出}


\subsection{}


\section{提案手法}

\subsection{}

\subsection{}

\subsection{}

\section{実験結果}
\subsection{}


\subsection{}


\section{今後の予定}

\newpage
\newpage 

\begin{thebibliography}{99}
\bibitem{Arai} T. Susuki and I. Arai, "Advance on underground radars," IEICE
Transactions, vol.E74, no.2, pp.289-294, 1991.
\bibitem{2007TCounts} T. Counts, A. C. Gurbuz, W. R. Scott Jr.,
        J. H. McClellan and K. Kim, "Multistatic
ground-penetrating radar experiments," IEEE Transrations on Geoscience and
Remote Sensing, vol. 45, no. 10, pp. 2544-2553, October 2007.
\bibitem{chichi} C-C Chen, S. Nag, W. D. Burnside, J. I. Halman,
K. A. Shubert and L. Peters, Jr., "A Standoff, Focused-Beam Land Mine Radar,"
IEEE Transactions on Geoscience and Remote Sensing, vol.38, no.1, pp. 507-514, 2000.
\bibitem{JeroenYarovoy} Jeroen Groenenboom, Alexander Yarovoy,
"Data Processing and Imaging in GPR System Dedicated for Landmine
Detection," Subsurface Sensing Technologies and Applications, vol.3,
        no.4, pp. 387-402, 2002.
\bibitem{YaroboyLighthart} Alexander G. Yarovoy and  Leo P. Ligthart,
"Polarimetric video impulse radar for landmine detection,"
Subsurface Sensing Technologies and Applications, vol.3, no.4, pp. 271-293, 2002.
\bibitem{2004MSato} M. Sato, Y. Hamada, X. Feng, F. N. Kong, Z. Zeng and
        G. Fang, "GPR using an array an-
tenna for land-mine detection," Near Subsurface Geophysics, vol. 2,
        pp. 7-13, 2004.
 \bibitem{2005Sato} M. Sato, K. Takahashi, X. Feng and
        T. Kobayashi, "Dual sensor alis evaluation test in
        Afghanistan," IEEE Geoscience and Remote Sensing Society
        Newsletter, pp. 22-24, September 2005.
 \bibitem{2009Sato} M. Sato, K. Takahashi, "Development of
        Dual Sensors and Deployment in Mine Affected
        Countries," in {\it Anti-personal Landmine Detection for
        Humanitarian Demining}, pp. 27-44, 2009.
\bibitem{2007SMas} S. Masuyama and A. Hirose, "Walled LTSA array for rapid, high spatial resolution,
and phase sensitive imaging to visualize plastic landmines," IEEE Transactions
on Geoscience and Remote Sensing, vol. 45, no. 8, pp. 2536-2543, August 2007.
\bibitem{2008SMas} S. Masuyama, K. Yasuda and A. Hirose, "Multiple mode selection of
walled-ltsa array elements for high resolution imaging to visualize antipersonnel
plastic landmines," IEEE Geoscience and Remote Sensing Letters, vol. 5,
        no. 4, pp. 745-749, October 2008.
\bibitem{2009Nakano} Y. Nakano and A. Hirose, "Improvement of plastic
        landmine visualization performance by use of ring-csom and
        frequency-domain local correlation," IEICE Transactions on
        Electronics, vol. E92-C, no. 1, pp. 102-108, January 2009.
\bibitem{2010Nakano} Y. Nakano and A. Hirose, "Adaptive identification of
        landmine class by evaluating the total degree of conformity of
        ring-SOM," Australian Journal of Intelligent Information
        Processing Systems, pp. 23-28, December 2010.
\bibitem{model} R. Karlina and M. Sato, "Model-Based Compressive Sensing Applied to Landmine Detection by GPR." IEICE Transaction, vol.E99-C, no.1 pp.44-51, 2016.
\end{thebibliography}

\end{document}